\subsubsubsection{LaTeX}

Install the complete version TeX Live:

\code{sudo apt install texlive-full}

In Visual Studio Code, install the extension: \texttt{LaTeX Workshop}

\subsubsubsubsection{Latex Workshop}

Open up the settings \texttt{JSON} file:

\code{Ctrl + Shift + P} and enter

\code{>Preferences: Open Settings (JSON)}

Some times, the recipes does not appear in the \texttt{JSON} file. Append the code below if it doesn't exist. 


\begin{minted}{latex}
    "latex-workshop.view.pdf.viewer": "browser",
    "latex-workshop.latex.autoBuild.run": "onSave",
    "latex-workshop.latex.autoClean.run": "onBuilt",
    "latex-workshop.latex.recipe.default": "first",
    "latex-workshop.chktex.run": "onType",
    "latex-workshop.chktex.delay": 2000,
    "latex-workshop.latex.recipes": [
        {
            "name": "latexmk",
            "tools": [
            "latexmk"
            ]
        },
        {
            "name": "pdflatex - bibtex - pdflatex x2",
            "tools": [
            "pdflatex",
            "bibtex",
            "pdflatex",
            "pdflatex"
            ]
        }
    ],
    "latex-workshop.latex.tools": [
        {
            "name": "latexmk",
            "command": "latexmk",
            "args": [
            "-synctex=1",
            "-interaction=nonstopmode",
            "-file-line-error",
            "-pdf",
            "-shell-escape",
            "-outdir=%OUTDIR%",
            "%DOC%"
            ],
            "env": {}
        },
        {
            "name": "pdflatex",
            "command": "pdflatex",
            "args": [
            "-synctex=1",
            "-interaction=nonstopmode",
            "-file-line-error",
            "%DOC%"
            ],
            "env": {}
        },
        {
            "name": "bibtex",
            "command": "bibtex",
            "args": [
            "%DOCFILE%"
            ],
            "env": {}
        }
    ]
    \end{minted}

\subsubsubsubsection{Default PDF viewer}

The setting

\code{"latex-workshop.view.pdf.viewer": "browser"}

will open up a browser tab when pressing the \texttt{View LaTeX PDF file} button. Using the browser works good with \code{Synctex} for jumping between PDF and code seamlessly.

\subsubsubsubsection{Synctex - Jump between PDF and code}

By having the flag \code{"-synctex=1"} in the recipe, one can enable jumping between the PDF and code locations seamlessly. Works good when using \code{"browser"} as default PDF viewer.

\begin{itemize}
    \item \code{Ctrl} clicking in the PDF.
    \item Set text marker in code and press \code{Ctrl + Alt + J}
\end{itemize}

\subsubsubsubsection{Default recipe}

The setting

\code{"latex-workshop.latex.recipe.default": "first"}

will run the first/top recipe given in \code{"latex-workshop.latex.recipes":}. It can be changed to \code{lastUsed} but might confuse some times.

Make sure that \code{latexmk} is the first item.


\subsubsubsubsection{Clean aux files}

The setting

\code{"latex-workshop.latex.autoClean.run": "onBuilt"}

will remove the \code{aux} files generated from the compilation after that the compilation is done.


\subsubsubsubsection{Chktex - Linting}

The settings

\code{"latex-workshop.chktex.run": "onType"}\\
\code{"latex-workshop.chktex.delay": 2000}

will enable linting using \code{Chtex}, checking two seconds after stopped writing. Will show problems in the \texttt{Problems} tab.

